%=============================================================================
% Chapter 9 Exercises - With hints from original book (9 exercises)
%=============================================================================
\section*{Exercises}
\addcontentsline{toc}{section}{Exercises}

\begin{enumerate}
    \item \label{exer1-chapter9}Let $A$ be a Dedekind domain, $S$ a multiplicatively closed subset of $A$. Show that $S^{-1}A$ is either a Dedekind domain or the field of fractions of $A$. If $S \not\subseteq A - \{0\}$, let $H, H'$ be the ideal class groups of $A$ and $S^{-1}A$ respectively. Show that extension of ideals induces a surjective homomorphism $H \to H'$.

    \item \label{exer2-chapter9}Let $A$ be a Dedekind domain. For a polynomial $f = a_0 + a_1 x + \cdots + a_n x^n \in A[x]$, the \emph{content} of $f$ is the ideal $c(f) = (a_0, \ldots, a_n)$. Prove \emph{Gauss's Lemma} that $c(fg) = c(f)c(g)$.
    
    \textit{Hint:} Localize at each maximal ideal.

    \item \label{exer3-chapter9}A valuation ring (which is not a field) is Noetherian if and only if it is a discrete valuation ring.

    \item \label{exer4-chapter9}Let $A$ be a local domain, not a field, with maximal ideal $\mathfrak{m}$. Suppose $\mathfrak{m}$ is principal and $\bigcap_{n=1}^\infty \mathfrak{m}^n = 0$. Prove that $A$ is a discrete valuation ring.

    \item \label{exer5-chapter9}Let $M$ be a finitely generated module over a Dedekind domain. Prove that $M$ is flat $\iff$ $M$ is torsion-free.
    
    \textit{Hint:} Use Chapter \ref{chapter3}, Exercise \ref{exer13-chapter3} and Chapter \ref{chapter7}, Exercise \ref{exer16-chapter7}.

    \item \label{exer6-chapter9}Let $M$ be a finitely generated torsion module over a Dedekind domain $A$ (so $T(M) = M$). Prove that $M$ is uniquely a direct sum of modules of the form $A/\mathfrak{p}_i^{n_i}$, where $\mathfrak{p}_i$ are non-zero prime ideals.\\
    \textit{Hint:} For each $\mathfrak{p} \neq 0$, $M_\mathfrak{p}$ is a torsion $A_\mathfrak{p}$-module; use the structure theorem for modules over a PID.

    \item \label{exer7-chapter9}Let $A$ be a Dedekind domain and $\mathfrak{a} \neq 0$ an ideal of $A$. Prove that every ideal in $A/\mathfrak{a}$ is principal.\\
    Deduce that every ideal in $A$ is generated by at most 2 elements.

    \item \label{exer8-chapter9}Let $\mathfrak{a}, \mathfrak{b}, \mathfrak{c}$ be three ideals in a Dedekind domain. Prove that
    \[\begin{aligned}
        \mathfrak{a} \cap (\mathfrak{b} + \mathfrak{c}) = (\mathfrak{a} \cap \mathfrak{b}) + (\mathfrak{a} \cap \mathfrak{c}),\\
        \mathfrak{a}(\mathfrak{b} \cap \mathfrak{c}) = (\mathfrak{a}\mathfrak{b}) \cap (\mathfrak{a}\mathfrak{c}).
    \end{aligned}
    \]
    \textit{Hint:} Localize.

    \item \label{exer9-chapter9}(Chinese Remainder Theorem) Let $\mathfrak{a}_1, \ldots, \mathfrak{a}_n$ be ideals in a Dedekind domain $A$, and let $x_1, \ldots, x_n \in A$. Prove that the system of congruences
    \[
    x \equiv x_i \pmod{\mathfrak{a}_i} \quad (1 \leq i \leq n)
    \]
    has a solution if and only if $x_i \equiv x_j \pmod{\mathfrak{a}_i + \mathfrak{a}_j}$ whenever $i \neq j$.\\
    \textit{Hint:} This is equivalent to saying that the sequence of $A$-modules
    \[
    0 \longrightarrow A \stackrel{\phi}{\longrightarrow} \bigoplus A/\mathfrak{a}_i \stackrel{\psi}{\longrightarrow} \bigoplus_{i < j} A/(\mathfrak{a}_i + \mathfrak{a}_j)
    \]
    is exact, where $\phi$ and $\psi$ are defined as follows:  
    \[ \phi(x) = (x + a_1, \ldots, x + a_n); \quad \psi(x_1 + a_1, \ldots, x_n + a_n) \] has $(i, j)$-component  
    \[ x_i - x_j + a_i + a_j. \] To show that this sequence is exact it is enough to show that  
    it is exact when localized at any $p \neq 0$: in other words we may assume that $A$ is a discrete valuation ring, and then it is easy.
\end{enumerate}
