%=============================================================================
% Chapter 10 Exercises - With hints from original book (12 exercises)
%=============================================================================
\section*{Exercises}
\addcontentsline{toc}{section}{Exercises}

\begin{enumerate}
    \item \label{exer1-chapter10}Let $\alpha_n \colon \Z/p\Z \to \Z/p^n\Z$ be the injective homomorphism of Abelian groups given by $\alpha_n(\bar{t}) = \overline{p^{n-1}t}$, and let $\alpha \colon A \to B$ be the direct sum of all $\alpha_n$. Show that the $p$-adic completion of $A$ is $A$ itself, but the completion of $A$ in the topology induced from the $p$-adic topology of $B$ is the direct product of infinitely many copies of $\Z/p\Z$. Deduce that $p$-adic completion is not a right-exact functor on the category of all $\Z$-modules.

    \item \label{exer2-chapter10}In Exercise \ref{exer1-chapter10}, let $A_n = \alpha^{-1}(p^n B)$. Consider the exact sequence
    \[
    0 \longrightarrow A_n \longrightarrow A \longrightarrow A/A_n \longrightarrow 0.
    \]
    Show that $\varprojlim$ is not right-exact, and compute $\varprojlim^1 A_n$.

    \item \label{exer3-chapter10}Let $A$ be a Noetherian ring, $\mathfrak{a}$ an ideal, and $M$ a finitely generated $A$-module. Use Krull's Theorem and Chapter \ref{chapter3}, Exercise \ref{exer14-chapter3} to show that
    \[
    \bigcap_{n=1}^\infty \mathfrak{a}^n M = \bigcap_{\mathfrak{m} \supseteq \mathfrak{a}} \Ker(M \to M_{\mathfrak{m}}),
    \]
    where $\mathfrak{m}$ runs through all maximal ideals of $A$ containing $\mathfrak{a}$.

    \quad\, Deduce that \[M = 0 \iff \Supp(M) \cap V(\mathfrak{a}) = \varnothing \quad (in \Spec(A)).\]
    \textit{Hint: } The reader should think of $\hat{M}$ as the ``Taylor expansion'' of $M$ transversal to the subscheme $V(\mathfrak{a})$: the above result then shows that $M$ is determined in a neighborhood of $V(\mathfrak{a})$ by its Taylor expansion.

    \item \label{exer4-chapter10}Let $A$ be a Noetherian ring, $\mathfrak{a}$ an ideal in $A$, and $\hat{A}$ the $\mathfrak{a}$-adic completion. For any $x \in A$, let $\hat{x}$ be the image of $x$ in $\hat{A}$. Show that
    \[
    x \text{ not a zero-divisor in } A \implies \hat{x} \text{ not a zero-divisor in } \hat{A}.
    \]
    Does this imply that
    \[
    A \text{ is an integral domain } \implies \hat{A} \text{ is an integral domain}?
    \]
    \textit{Hint:} Apply the exactness of completion to the sequence $0 \longrightarrow A \stackrel{x}{\longrightarrow} A$.

    \item \label{exer5-chapter10}Let $A$ be a Noetherian ring and let $\mathfrak{a}$, $\mathfrak{b}$ be ideals in $A$. If $M$ is any $A$-module, let $M^{\mathfrak{a}}$, $M^{\mathfrak{b}}$ denote its $\mathfrak{a}$-adic and $\mathfrak{b}$-adic completions respectively. If $M$ is finitely generated, prove that $(M^{\mathfrak{a}})^{\mathfrak{b}} \cong M^{\mathfrak{a}+\mathfrak{b}}$.
    
    \textit{hint:} Take the $\mathfrak{a}$-adic completion of the exact sequence
    \[
    0 \to \mathfrak{b}^m M \to M/\mathfrak{b}^m M \to 0
    \]
    and apply \eqref{pro:completion-tensor}. Then use the isomorphism
    \[
    \varprojlim_m \left( \varprojlim_n M/(\mathfrak{a}^n M + \mathfrak{b}^m M) \right) \cong \varprojlim_n M/(\mathfrak{a}^n M + \mathfrak{b}^n M)
    \]
    and the inclusions $(\mathfrak{a}+\mathfrak{b})^{2n} \subseteq \mathfrak{a}^n + \mathfrak{b}^n \subseteq (\mathfrak{a}+\mathfrak{b})^n$.

    \item \label{exer6-chapter10}Let $A$ be a Noetherian ring and $\mathfrak{a}$ an ideal in $A$. Prove that $\mathfrak{a}$ is contained in the Jacobson radical of $A$ if and only if every maximal ideal of $A$ is closed for the $\mathfrak{a}$-topology. (A Noetherian topological ring in which the topology is defined by an ideal contained in the Jacobson radical is called a \emph{Zariski ring}\index{Zariski, ring}. Examples are local rings and (by~\eqref{prop:10.15}(iv)) $\mathfrak{a}$-adic completions.)

    \item \label{exer7-chapter10}Let $A$ be a Noetherian ring, $\mathfrak{a}$ an ideal of $A$, and $\hat{A}$ the $\mathfrak{a}$-adic completion. Prove that $\hat{A}$ is faithfully flat over $A$ (Chapter \ref{chapter3} Exercise \ref{exer16-chapter3}) if and only if $A$ is a Zariski ring (for the $\mathfrak{a}$-topology).
    
    \textit{Hint:} Since $\hat{A}$ is flat over $A$, it is enough to show that
    \[
    M \to \hat{M} \text{ injective for all finitely generated } M \Leftrightarrow A \text{ is Zariski};
    \]
    now use~\eqref{cor:10.19} and Exercise \ref{exer6-chapter10}.

    \item \label{exer8-chapter10}Let $A$ be the local ring of the origin in $\C^n$ (i.e., the ring of all rational functions $f/g \in \C(z_1, \ldots, z_n)$ with $g(0) \neq 0$), let $B$ be the ring of power series in $z_1, \ldots, z_n$ which converge in some neighborhood of the origin, and let $C$ be the ring of formal power series in $z_1, \ldots, z_n$, so that $A \subset B \subset C$. Show that $B$ is a local ring and that its completion for the maximal ideal topology is $C$. Assuming that $B$ is Noetherian, prove that $B$ is $A$-flat. 
    
    \textit{Hint:} Use Chapter \ref{chapter3}, Exercise \ref{exer17-chapter3}, and Exercise \ref{exer7-chapter10} above.

    \item \label{exer9-chapter10} Let $A$ be a local ring, $\mathfrak{m}$ its maximal ideal. Assume that $A$ is $\mathfrak{m}$-adically complete. For any polynomial $f(x) \in A[x]$, let $\bar{f}(x) \in (A/\mathfrak{m})[x]$ denote its reduction mod.\ $\mathfrak{m}$. Prove \emph{Hensel's lemma}\index{Hensel's Lemma}: if $f(x)$ is monic of degree $n$ and if there exist coprime monic polynomials $\bar{g}(x)$, $\bar{h}(x) \in (A/\mathfrak{m})[x]$ of degrees $r$, $n-r$ with $\bar{f}(x) = \bar{g}(x)\bar{h}(x)$, then we can lift $\bar{g}(x)$, $\bar{h}(x)$ back to monic polynomials $g(x)$, $h(x) \in A[x]$ such that $f(x) = g(x)h(x)$.
    
    \textit{Hint:} Assume inductively that we have constructed $g_k(x)$, $h_k(x) \in A[x]$ such that $g_k(x)h_k(x) - f(x) \in \mathfrak{m}^k A[x]$. Then use the fact that since $\bar{g}(x)$ and $\bar{h}(x)$ are coprime we can find $\bar{a}_p(x)$, $\bar{b}_p(x)$, of degrees $\le n-r$, $r$ respectively, such that $x^p = \bar{a}_p(x)\bar{g}_k(x) + \bar{b}_p(x)\bar{h}_k(x)$, where $p$ is any integer such that $1 \le p \le n$. Finally, use the completeness of $A$ to show that the sequences $g_k(x)$, $h_k(x)$ converge to the required $g(x)$, $h(x)$.

    \item \label{exer10-chapter10}\begin{enumerate}[i)]
        \item With the notation of Exercise \ref{exer9-chapter10}, deduce from Hensel's Lemma that if $\bar{f}(x)$ has a simple root $\bar{a} \in A/\mathfrak{m}$, then $f(x)$ has a simple root $a \in A$ such that $\bar{a} \equiv a \pmod{\mathfrak{m}}$.
        \item Show that $2$ is a square in the ring of $7$-adic integers.
        \item Let $f(x, y) \in k[x, y]$ where $k$ is a field. Suppose $f(0, y)$ has $y = a_0$ as a simple root. Show that there exists a formal power series $y(x) = \sum_{n=0}^\infty a_n x^n$ such that $f(x, y(x)) = 0$.
    \end{enumerate}
    (This gives the ``analytic branch'' of the curve $f = 0$ through the point $(0, a_0)$.)

    \item Show that the converse of \eqref{thm:10.26} is false, even if one assumes that $A$ is a local ring and that $\widehat{A}$ is a finitely generated $A$-module. 
    
    \textit{Hint:} Take $A$ to be the ring of germs of $C^{\infty}$ functions of $x$ at $x = 0$, and use Borel's Theorem that every power series occurs as the Taylor expansion of some $C^{\infty}$ function.

    \item If $A$ is Noetherian, then $A[[x_1, \ldots, x_n]]$ is a faithfully flat $A$-algebra. 
    
    \textit{Hint:} Express $A \to A[[x_1, \ldots, x_n]]$ as a composition of flat extensions, and use Exercise \ref{exer5-chapter1}(v) of Chapter \ref{chapter1}.
\end{enumerate}
