\chapter{Integral Dependence and Valuations}\label{chapter5}

In classical algebraic geometry curves were frequently studied by projecting them onto a line and regarding the curve as a (ramified) covering of the line. This is quite analogous to the relationship between a number field and the rational field---or rather between their rings of integers---and the common algebraic feature is the notion of integral dependence. In this chapter we prove a number of results about integral dependence. In particular we prove the theorems of Cohen-Seidenberg (the ``going-up'' and ``going-down'' theorems) concerning prime ideals in an integral extension. In the exercises at the end we discuss the algebro-geometric situation and in particular the Normalization Lemma.

We also give a brief treatment of valuations.

\section*{Integral Dependence}
\addcontentsline{toc}{section}{Integral Dependence}
Let $B$ be a ring, $A$ a subring of $B$ (so that $1 \in A$). An element $x$ of $B$ is said to be \emph{integral over $A$} if $x$ is a root of a monic polynomial with coefficients in $A$, that is if $x$ satisfies an equation of the form
\begin{equation}\label{eq:integral-eq}
x^n + a_1 x^{n-1} + \cdots + a_n = 0 \tag{1}
\end{equation}
where the $a_i$ are elements of $A$. Clearly every element of $A$ is integral over $A$.

\setcounter{theorem}{-1}
\begin{examplenumbered}\label{ex:5.0}
$A = \Z$, $B = \Q$. If a rational number $x = r/s$ is integral over $\Z$, where $r, s$ have no common factor, we have from \eqref{eq:integral-eq}
\[
r^n + a_1 r^{n-1} s + \cdots + a_n s^n = 0
\]
the $a_i$ being rational integers. Hence $s$ divides $r^n$, hence $s = \pm 1$, hence $x \in \Z$.
\end{examplenumbered}

\begin{proposition}\label{prop:5.1}\index{integral element!characterization}
The following are equivalent:
\begin{enumerate}
    \item[i)] $x \in B$ is integral over $A$;
    \item[ii)] $A[x]$ is a finitely generated $A$-module;
    \item[iii)] $A[x]$ is contained in a subring $C$ of $B$ such that $C$ is a finitely generated $A$-module;
    \item[iv)] There exists a faithful $A[x]$-module $M$ which is finitely generated as an $A$-module.
\end{enumerate}
\end{proposition}

\begin{proof}
    i) $\implies$ ii). From \eqref{eq:integral-eq} we have
    \[
    x^{n+r} = -a_1 x^{n+r-1} - \cdots - a_n x^r
    \]
    for all $r \geq 0$; hence, by induction, all positive powers of $x$ lie in the $A$-module generated by $1, x, \ldots, x^{n-1}$. Hence $A[x]$ is generated (as an $A$-module) by $1, x, \ldots, x^{n-1}$.

    ii) $\implies$ iii). Take $C = A[x]$.

    iii) $\implies$ iv). Take $M = C$, which is a faithful $A[x]$-module (since $yC = 0 \implies y \cdot 1 = 0$).

    iv) $\implies$ i). This follows from \eqref{prop:module-endomorphism-equation}: take $\phi$ to be multiplication by $x$, and $\mathfrak{a} = A$ (we have $xM \subseteq M$ since $M$ is an $A[x]$-module); since $M$ is faithful, we have $x^n + a_1 x^{n-1} + \cdots + a_n = 0$ for suitable $a_i \in A$.
\end{proof}

\begin{corollary}\label{cor:5.2}
    Let $x_i$ ($1 \leq i \leq n$) be elements of $B$, each integral over $A$. Then the ring $A[x_1, \ldots, x_n]$ is a finitely-generated $A$-module.
\end{corollary}

\begin{proof}
    By induction on $n$. The case $n = 1$ is part of \eqref{prop:5.1}. Assume $n > 1$, let $A_r = A[x_1, \ldots, x_r]$; then by the inductive hypothesis $A_{n-1}$ is a finitely generated $A$-module. $A_n = A_{n-1}[x_n]$ is a finitely generated $A_{n-1}$-module (by the case $n = 1$, since $x_n$ is integral over $A_{n-1}$). Hence by \eqref{prop:finitely-generated-restriction}, $A_n$ is finitely generated as an $A$-module.
\end{proof}

\begin{corollary}\label{cor:5.3}\index{integral closure}
    The set $C$ of elements of $B$ which are integral over $A$ is a subring of $B$ containing $A$.
\end{corollary}

\begin{proof}
    If $x, y \in C$ then $A[x, y]$ is a finitely generated $A$-module by \eqref{cor:5.2}. Hence $x \pm y$ and $xy$ are integral over $A$, by (iii) of \eqref{prop:5.1}.
\end{proof}

The ring $C$ in \eqref{cor:5.3} is called the \emph{integral closure} of $A$ in $B$.\index{integral closure} If $C = A$, then $A$ is said to be \emph{integrally closed} in $B$.\index{integrally closed} If $C = B$, the ring $B$ is said to be \emph{integral} over $A$.

\begin{remark}
    Let $f \colon A \to B$ be a ring homomorphism, so that $B$ is an $A$-algebra. Then $f$ is said to be \emph{integral}, and $B$ is said to be an \emph{integral $A$-algebra}, if $B$ is integral over its subring $f(A)$. In this terminology, the above results show that
    \[
    \text{finite type} + \text{integral} = \text{finite}.
    \]
\end{remark}

\begin{corollary}\label{cor:5.4}
    If $A \subseteq B \subseteq C$ are rings and if $B$ is integral over $A$, and $C$ is integral over $B$, then $C$ is integral over $A$ (transitivity of integral dependence).
\end{corollary}

\begin{proof}
    Let $x \in C$, then we have an equation
    \[
    x^n + b_1 x^{n-1} + \cdots + b_n = 0 \qquad (b_i \in B).
    \]
    The ring $B' = A[b_1, \ldots, b_n]$ is a finitely generated $A$-module by \eqref{cor:5.2}, and $B'[x]$ is a finitely generated $B'$-module (since $x$ is integral over $B'$). Hence $B'[x]$ is a finitely generated $A$-module by \eqref{prop:finitely-generated-restriction} and therefore $x$ is integral over $A$ by (iii) of \eqref{prop:5.1}.
\end{proof}

\begin{corollary}\label{cor:5.5}
Let $A \subseteq B$ be rings and let $C$ be the integral closure of $A$ in $B$. Then $C$ is integrally closed in $B$.
\end{corollary}

\begin{proof}
    Let $x \in B$ be integral over $C$. By \eqref{cor:5.4}, $x$ is integral over $A$, hence $x \in C$.
\end{proof}

The next proposition shows that integral dependence is preserved on passing to quotients and to rings of fractions:

\begin{proposition}\label{prop:5.6}
Let $A \subseteq B$ be rings, $B$ integral over $A$.
\begin{enumerate}
    \item[i)] \label{item 1:prop:5.6} If $\mathfrak{b}$ is an ideal of $B$ and $\mathfrak{a} = \mathfrak{b}^c = A \cap \mathfrak{b}$, then $B/\mathfrak{b}$ is integral over $A/\mathfrak{a}$.
    \item[ii)] \label{item 2:prop:5.6} If $S$ is a multiplicatively closed subset of $A$, then $S^{-1}B$ is integral over $S^{-1}A$.
\end{enumerate}
\end{proposition}

\begin{proof}
i) If $x \in B$ we have, say, $x^n + a_1 x^{n-1} + \cdots + a_n = 0$, with $a_i \in A$. Reduce this equation mod~$\mathfrak{b}$.

ii) Let $x/s \in S^{-1}B$ ($x \in B$, $s \in S$). Then the equation above gives
\[
(x/s)^n + (a_1/s)(x/s)^{n-1} + \cdots + a_n/s^n = 0
\]
which shows that $x/s$ is integral over $S^{-1}A$.
\end{proof}

\section*{The Going-Up Theorem}
\addcontentsline{toc}{section}{The Going-Up Theorem}

\begin{proposition}\label{prop:5.7}\index{integral extension!field criterion}
Let $A \subseteq B$ be integral domains, $B$ integral over $A$. Then $B$ is a field if and only if $A$ is a field.
\end{proposition}

\begin{proof}
Suppose $A$ is a field; let $y \in B$, $y \neq 0$. Let
\[
y^n + a_1 y^{n-1} + \cdots + a_n = 0
\]
be an equation of integral dependence for $y$ of smallest possible degree. Since $B$ is an integral domain we have $a_n \neq 0$, hence $y^{-1} = -a_n^{-1}(y^{n-1} + a_1 y^{n-2} + \cdots + a_{n-1}) \in B$. Hence $B$ is a field.

Conversely, suppose $B$ is a field; let $x \in A$, $x \neq 0$. Then $x^{-1} \in B$, hence is integral over $A$, so that we have an equation
\[
x^{-m} + a'_1 x^{-m+1} + \cdots + a'_m = 0 \qquad (a'_i \in A).
\]
It follows that $x^{-1} = -(a'_1 + a'_2 x + \cdots + a'_m x^{m-1}) \in A$, hence $A$ is a field.
\end{proof}

\begin{corollary}\label{cor:5.8}
    Let $A \subseteq B$ be rings, $B$ integral over $A$; let $\mathfrak{q}$ be a prime ideal of $B$ and let $\mathfrak{p} = \mathfrak{q}^c = \mathfrak{q} \cap A$. Then $\mathfrak{q}$ is maximal if and only if $\mathfrak{p}$ is maximal.
\end{corollary}

\begin{proof}
    By \eqref{prop:5.6}, $B/\mathfrak{q}$ is integral over $A/\mathfrak{p}$, and both these rings are integral domains. Now use \eqref{prop:5.7}.
\end{proof}

\begin{corollary}\label{cor:5.9}
    Let $A \subseteq B$ be rings, $B$ integral over $A$; let $\mathfrak{q}, \mathfrak{q}'$ be prime ideals of $B$ such that $\mathfrak{q} \subseteq \mathfrak{q}'$ and $\mathfrak{q}^c = \mathfrak{q}'^c = \mathfrak{p}$ say. Then $\mathfrak{q} = \mathfrak{q}'$.
\end{corollary}

\begin{proof}
    By \eqref{prop:5.6}, $B/\mathfrak{q}$ is integral over $A/\mathfrak{p}$. Let $\mathfrak{m}$ be the extension of $\mathfrak{p}$ in $A/\mathfrak{p}$ and let $\mathfrak{n}, \mathfrak{n}'$ be the extensions of $\mathfrak{q}, \mathfrak{q}'$ respectively in $B/\mathfrak{q}$. Then $\mathfrak{m}$ is the maximal ideal of $A/\mathfrak{p}$; $\mathfrak{n} \subseteq \mathfrak{n}'$, and $\mathfrak{n}^c = \mathfrak{n}'^c = \mathfrak{m}$. By \eqref{cor:5.8} it follows that $\mathfrak{n}, \mathfrak{n}'$ are maximal, hence $\mathfrak{n} = \mathfrak{n}'$, hence by \eqref{prop:extension-ideals}\eqref{item 4:prop:extension-ideals}, $\mathfrak{q} = \mathfrak{q}'$.
\end{proof}

\begin{theorem}\label{thm:5.10}\index{lying over}
    Let $A \subseteq B$ be rings, $B$ integral over $A$, and let $\mathfrak{p}$ be a prime ideal of $A$. Then there exists a prime ideal $\mathfrak{q}$ of $B$ such that $\mathfrak{q} \cap A = \mathfrak{p}$.
\end{theorem}
\begin{proof}
    By \eqref{prop:5.6}, $B_{\mathfrak{p}}$ is integral over $A_{\mathfrak{p}}$, and the diagram
    \[\begin{tikzcd}
        A & B \\
        {A_{\mathfrak{p}}} & {B_{\mathfrak{p}}}
        \arrow[from=1-1, to=1-2]
        \arrow["\alpha"', from=1-1, to=2-1]
        \arrow["\beta", from=1-2, to=2-2]
        \arrow[from=2-1, to=2-2]
    \end{tikzcd}\]
    (in which the horizontal arrows are injections) is commutative. Let $\mathfrak{n}$ be a maximal ideal of $B_{\mathfrak{p}}$; then $\mathfrak{m} = \mathfrak{n} \cap A_{\mathfrak{p}}$ is maximal by \eqref{cor:5.8}, hence is the unique maximal ideal of the local ring $A_{\mathfrak{p}}$. If $\mathfrak{q} = \beta^{-1}(\mathfrak{n})$, then $\mathfrak{q}$ is prime and we have $\mathfrak{q} \cap A = \alpha^{-1}(\mathfrak{m}) = \mathfrak{p}$.
\end{proof}

\begin{theorem}[Going-Up Theorem]\label{thm:5.11}\index{Going-Up Theorem}\index{integral extension!going-up}
Let $A \subseteq B$ be rings, $B$ integral over $A$; let $\mathfrak{p}_1 \subseteq \cdots \subseteq \mathfrak{p}_n$ be a chain of prime ideals of $A$ and $\mathfrak{q}_1 \subseteq \cdots \subseteq \mathfrak{q}_m$ ($m < n$) a chain of prime ideals of $B$ such that $\mathfrak{q}_i \cap A = \mathfrak{p}_i$ ($1 \leq i \leq m$). Then the chain $\mathfrak{q}_1 \subseteq \cdots \subseteq \mathfrak{q}_m$ can be extended to a chain $\mathfrak{q}_1 \subseteq \cdots \subseteq \mathfrak{q}_n$ such that $\mathfrak{q}_i \cap A = \mathfrak{p}_i$ for $1 \leq i \leq n$.
\end{theorem}

\begin{proof}
By induction we reduce immediately to the case $m = 1$, $n = 2$. Let $\overline{A} = A/\mathfrak{p}_1$, $\overline{B} = B/\mathfrak{q}_1$; then $\overline{A} \subseteq \overline{B}$, and $\overline{B}$ is integral over $\overline{A}$ by \eqref{prop:5.6}. Hence, by \eqref{thm:5.10}, there exists a prime ideal $\overline{\mathfrak{q}}_2$ of $\overline{B}$ such that $\overline{\mathfrak{q}}_2 \cap \overline{A} = \overline{\mathfrak{p}}_2$, the image of $\mathfrak{p}_2$ in $\overline{A}$. Lift back $\overline{\mathfrak{q}}_2$ to $B$ and we have a prime ideal $\mathfrak{q}_2$ with the required properties.
\end{proof}

\section*{Integrally Closed Integral Domains. The Going-Down Theorem}
\addcontentsline{toc}{section}{eIntegrally Closed Integral Domains. The Going-Down Theorem}

\eqref{prop:5.6} can be sharpened:

\begin{proposition}\label{prop:5.12}
Let $A \subseteq B$ be rings, $C$ the integral closure of $A$ in $B$. Let $S$ be a multiplicatively closed subset of $A$. Then $S^{-1}C$ is the integral closure of $S^{-1}A$ in $S^{-1}B$.
\end{proposition}

\begin{proof}
By \eqref{prop:5.6}, $S^{-1}C$ is integral over $S^{-1}A$. Conversely, if $b/s \in S^{-1}B$ is integral over $S^{-1}A$, then we have an equation of the form
\[
(b/s)^n + (a_1/s_1)(b/s)^{n-1} + \cdots + a_n/s_n = 0
\]
where $a_i \in A$, $s_i \in S$ ($1 \leq i \leq n$). Let $t = s_1 \cdots s_n$ and multiply this equation by $(st)^n$ throughout. Then it becomes an equation of integral dependence for $bt$ over $A$. Hence $bt \in C$ and therefore $b/s = bt/st \in S^{-1}C$.
\end{proof}

An integral domain is said to be \emph{integrally closed} (without qualification) if it is integrally closed in its field of fractions.\index{integrally closed domain} For example, $\Z$ is integrally closed (see Example \eqref{ex:5.0}). The same argument shows that any unique factorization domain is integrally closed. In particular, a polynomial ring $k[x_1, \ldots, x_n]$ over a field is integrally closed.

Integral closure is a local property:

\begin{proposition}\label{prop:5.13}\index{integrally closed!local property}
Let $A$ be an integral domain. Then the following are equivalent:
\begin{enumerate}
    \item[i)] $A$ is integrally closed;
    \item[ii)] $A_{\mathfrak{p}}$ is integrally closed, for each prime ideal $\mathfrak{p}$;
    \item[iii)] $A_{\mathfrak{m}}$ is integrally closed, for each maximal ideal $\mathfrak{m}$.
\end{enumerate}
\end{proposition}
\begin{proof}
    Let $K$ be the field of fractions of $A$, let $C$ be the integral closure of $A$ in $K$, and let $f \colon A \to C$ be the identity mapping of $A$ into $C$. Then $A$ is integrally closed $\iff$ $f$ is surjective, and by \eqref{prop:5.12}, $A_{\mathfrak{p}}$ (resp.~$A_{\mathfrak{m}}$) is integrally closed $\iff$ $f_{\mathfrak{p}}$ (resp.~$f_{\mathfrak{m}}$) is surjective. Now use \eqref{prop:injective-surjective-local}.
\end{proof}

Let $A \subseteq B$ be rings and let $\mathfrak{a}$ be an ideal of $A$. An element of $B$ is said to be \emph{integral over $\mathfrak{a}$} if it satisfies an equation of integral dependence over $A$ in which all the coefficients lie in $\mathfrak{a}$. The \emph{integral closure} of $\mathfrak{a}$ in $B$ is the set of all elements of $B$ which are integral over $\mathfrak{a}$.

\begin{lemma}\label{lem:5.14}
Let $C$ be the integral closure of $A$ in $B$ and let $\mathfrak{a}^e$ denote the extension of $\mathfrak{a}$ in $C$. Then the integral closure of $\mathfrak{a}$ in $B$ is the radical of $\mathfrak{a}^e$ (and is therefore closed under addition and multiplication).
\end{lemma}

\begin{proof}
If $x \in B$ is integral over $\mathfrak{a}$, we have an equation of the form
\[
x^n + a_1 x^{n-1} + \cdots + a_n = 0
\]
with $a_1, \ldots, a_n$ in $\mathfrak{a}$. Hence $x \in C$ and $x^n \in \mathfrak{a}^e$, that is $x \in r(\mathfrak{a}^e)$. Conversely, if $x \in r(\mathfrak{a}^e)$ then $x^n = \sum a_i x_i$ for some $n > 0$, where the $a_i$ are elements of $\mathfrak{a}$ and the $x_i$ are elements of $C$. Since each $x_i$ is integral over $A$ it follows from \eqref{cor:5.2} that $M = A[x_1, \ldots, x_n]$ is a finitely generated $A$-module, and we have $x^n M \subseteq \mathfrak{a} M$. Hence by \eqref{prop:module-endomorphism-equation} (taking $\phi$ there to be multiplication by $x^n$) we see that $x^n$ is integral over $\mathfrak{a}$, hence $x$ is integral over $\mathfrak{a}$.
\end{proof}

\begin{proposition}\label{prop:5.15}
    Let $A \subseteq B$ be integral domains, $A$ integrally closed, and let $x \in B$ be integral over an ideal $\mathfrak{a}$ of $A$. Then $x$ is algebraic over the field of fractions $K$ of $A$, and if its minimal polynomial over $K$ is $t^n + a_1 t^{n-1} + \cdots + a_n$, then $a_1, \ldots, a_n$ lie in $r(\mathfrak{a})$.
\end{proposition}

\begin{proof}
Clearly $x$ is algebraic over $K$. Let $L$ be an extension field of $K$ which contains all the conjugates $x_1, \ldots, x_n$ of $x$. Each $x_i$ satisfies the same equation of integral dependence as $x$ does, hence each $x_i$ is integral over $\mathfrak{a}$. The coefficients of the minimal polynomial of $x$ over $K$ are polynomials in the $x_i$, hence by \eqref{lem:5.14} are integral over $\mathfrak{a}$. Since $A$ is integrally closed, they must lie in $r(\mathfrak{a})$, by \eqref{lem:5.14} again.
\end{proof}

\begin{theorem}[Going-Down Theorem]\label{thm:5.16}\index{Going-Down Theorem}\index{integral extension!going-down}
Let $A \subseteq B$ be integral domains, $A$ integrally closed, $B$ integral over $A$. Let $\mathfrak{p}_1 \supseteq \cdots \supseteq \mathfrak{p}_n$ be a chain of prime ideals of $A$, and let $\mathfrak{q}_1 \supseteq \cdots \supseteq \mathfrak{q}_m$ ($m < n$) be a chain of prime ideals of $B$ such that $\mathfrak{q}_i \cap A = \mathfrak{p}_i$ ($1 \leq i \leq m$). Then the chain $\mathfrak{q}_1 \supseteq \cdots \supseteq \mathfrak{q}_m$ can be extended to a chain $\mathfrak{q}_1 \supseteq \cdots \supseteq \mathfrak{q}_n$ such that $\mathfrak{q}_i \cap A = \mathfrak{p}_i$ ($1 \leq i \leq n$).
\end{theorem}

\begin{proof}
    As in \eqref{thm:5.11} we reduce immediately to the case $m = 1$, $n = 2$. Then we have to show that $\mathfrak{p}_2$ is the contraction of a prime ideal in the ring $B_{\mathfrak{q}_1}$, or equivalently \eqref{prop:contracted-ideal} that $B_{\mathfrak{q}_1} \mathfrak{p}_2 \cap A = \mathfrak{p}_2$.

    Every $x \in B_{\mathfrak{q}_1} \mathfrak{p}_2$ is of the form $y/s$, where $y \in B \mathfrak{p}_2$ and $s \in B - \mathfrak{q}_1$. By \eqref{lem:5.14}, $y$ is integral over $\mathfrak{p}_2$, and hence by \eqref{prop:5.15} its minimal equation over $K$, the field of fractions of $A$, is of the form
    \begin{equation}\label{eq:5.16-1}
    y^r + u_1 y^{r-1} + \cdots + u_r = 0 \tag{1}
    \end{equation}
    with $u_1, \ldots, u_r$ in $\mathfrak{p}_2$.

    Now suppose that $x \in B_{\mathfrak{q}_1} \mathfrak{p}_2 \cap A$. Then $s = y x^{-1}$ with $x^{-1} \in K$, so that the minimal equation for $s$ over $K$ is obtained by dividing \eqref{eq:5.16-1} by $x^r$, and is therefore, say,
    \begin{equation}\label{eq:5.16-2}
    s^r + v_1 s^{r-1} + \cdots + v_r = 0 \tag{2}
    \end{equation}
    where $v_i = u_i / x^i$. Consequently
    \begin{equation}\label{eq:5.16-3}
    x^i v_i = u_i \in \mathfrak{p}_2 \qquad (1 \leq i \leq r) \tag{3}.
    \end{equation}

    But $s$ is integral over $A$, hence by \eqref{prop:5.15} (with $\mathfrak{a} = (1)$) each $v_i$ is in $A$. Suppose $x \notin \mathfrak{p}_2$. Then \eqref{eq:5.16-3} shows that each $v_i \in \mathfrak{p}_2$, hence \eqref{eq:5.16-2} shows that $s^r \in B \mathfrak{p}_2 \subseteq B \mathfrak{p}_1 \subseteq \mathfrak{q}_1$, and therefore $s \in \mathfrak{q}_1$, which is a contradiction. Hence $x \in \mathfrak{p}_2$ and therefore $B_{\mathfrak{q}_1} \mathfrak{p}_2 \cap A = \mathfrak{p}_2$ as required.
\end{proof}

The proof of the next proposition assumes some standard facts from field theory.

\begin{proposition}\label{prop:5.17}
    Let $A$ be an integrally closed domain, $K$ its field of fractions, $L$ a finite separable algebraic extension of $K$, $B$ the integral closure of $A$ in $L$. Then there exists a basis $v_1, \ldots, v_n$ of $L$ over $K$ such that $B \subseteq \sum_{i=1}^n A v_i$.
\end{proposition}

\begin{proof}
If $v$ is any element of $L$, then $v$ is algebraic over $K$ and therefore satisfies an equation of the form
\[
a_0 v^r + a_1 v^{r-1} + \cdots + a_r = 0 \qquad (a_i \in A).
\]
Multiplying this equation by $a_0^{r-1}$, we see that $a_0 v = u$ is integral over $A$, and hence is in $B$. Thus, given any basis of $L$ over $K$ we may multiply the basis elements by suitable elements of $A$ to get a basis $u_1, \ldots, u_n$ such that each $u_i \in B$.

Let $T$ denote trace (from $L$ to $K$). Since $L/K$ is separable, the bilinear form $(x, y) \mapsto T(xy)$ on $L$ (considered as a vector space over $K$) is non-degenerate, and hence we have a dual basis $v_1, \ldots, v_n$ of $L$ over $K$, defined by $T(u_i v_j) = \delta_{ij}$. Let $x \in B$, say $x = \sum x_i v_i$ ($x_i \in K$). We have $x u_i \in B$ (since $u_i \in B$) and therefore $T(x u_i) \in A$ by \eqref{prop:5.15} (for the trace of an element is a multiple of one of the coefficients in the minimal polynomial). But $T(x u_i) = \sum_j T(x_j u_i v_j) = \sum_j x_j T(u_i v_j) = \sum_j x_j \delta_{ij} = x_i$, hence $x_i \in A$. Consequently $B \subseteq \sum_i A v_i$.
\end{proof}

\section*{Valuation Rings}
\addcontentsline{toc}{section}{Valuation Rings}

Let $B$ be an integral domain, $K$ its field of fractions. $B$ is a \emph{valuation ring}\index{valuation ring} of $K$ if, for each $x \neq 0$, either $x \in B$ or $x^{-1} \in B$ (or both).\index{valuation ring}

\begin{proposition}\label{prop:5.18}\index{valuation ring!properties}
\begin{enumerate}
    \item[i)] $B$ is a local ring.
    \item[ii)] If $B'$ is a ring such that $B \subseteq B' \subseteq K$, then $B'$ is a valuation ring of $K$.
    \item[iii)] $B$ is integrally closed (in $K$).
\end{enumerate}
\end{proposition}

\begin{proof}
    i) Let $\mathfrak{m}$ be the set of non-units of $B$, so that $x \in \mathfrak{m} \iff$ either $x = 0$ or $x^{-1} \notin B$. If $a \in B$ and $x \in \mathfrak{m}$ we have $ax \in \mathfrak{m}$, for otherwise $(ax)^{-1} \in B$ and therefore $x^{-1} = a \cdot (ax)^{-1} \in B$. Next let $x, y$ be non-zero elements of $\mathfrak{m}$. Then either $x y^{-1} \in B$ or $x^{-1} y \in B$. If $x y^{-1} \in B$ then $x + y = (1 + x y^{-1})y \in B \mathfrak{m} \subseteq \mathfrak{m}$, and similarly if $x^{-1} y \in B$. Hence $\mathfrak{m}$ is an ideal and therefore $B$ is a local ring by \eqref{prop:local-ring-characterization}.

    ii) Clear from the definitions.

    iii) Let $x \in K$ be integral over $B$. Then we have, say,
    \[
    x^n + b_1 x^{n-1} + \cdots + b_n = 0
    \]
    with the $b_i \in B$. If $x \in B$ there is nothing to prove. If not, then $x^{-1} \in B$, hence $x = -(b_1 + b_2 x^{-1} + \cdots + b_n x^{1-n}) \in B$.
\end{proof}

Let $K$ be a field, $\Omega$ an algebraically closed field. Let $\Sigma$ be the set of all pairs $(A, f)$, where $A$ is a subring of $K$ and $f$ is a homomorphism of $A$ into $\Omega$. We partially order the set $\Sigma$ as follows:
\[
(A, f) \leq (A', f') \quad \iff \quad A \subseteq A' \text{ and } f'|_A = f.
\]
The conditions of Zorn's lemma are clearly satisfied and therefore the set $\Sigma$ has at least one maximal element.

Let $(B, g)$ be a maximal element of $\Sigma$. We want to prove that $B$ is a valuation ring of $K$. The first step in the proof is

\begin{lemma}\label{lem:5.19}
$B$ is a local ring and $\mathfrak{m} = \Ker(g)$ is its maximal ideal.
\end{lemma}

\begin{proof}
Since $g(B)$ is a subring of a field and therefore an integral domain, the ideal $\mathfrak{m} = \Ker(g)$ is prime. We can extend $g$ to a homomorphism $\bar{g} \colon B_{\mathfrak{m}} \to \Omega$ by putting $\bar{g}(b/s) = g(b)/g(s)$ for all $b \in B$ and all $s \in B - \mathfrak{m}$, since $g(s)$ will not be zero. Since the pair $(B, g)$ is maximal it follows that $B = B_{\mathfrak{m}}$, hence $B$ is a local ring and $\mathfrak{m}$ is its maximal ideal.
\end{proof}

\begin{lemma}\label{lem:5.20}
Let $x$ be a non-zero element of $K$. Let $B[x]$ be the subring of $K$ generated by $x$ over $B$, and let $\mathfrak{m}[x]$ be the extension of $\mathfrak{m}$ in $B[x]$. Then either $\mathfrak{m}[x] \neq B[x]$ or $\mathfrak{m}[x^{-1}] \neq B[x^{-1}]$.
\end{lemma}

\begin{proof}
Suppose that $\mathfrak{m}[x] = B[x]$ and $\mathfrak{m}[x^{-1}] = B[x^{-1}]$. Then we shall have equations
\begin{align}
u_0 + u_1 x + \cdots + u_m x^m &= 1 \qquad (u_i \in \mathfrak{m})  \tag{1}\label{eq:5.20-1} \\
v_0 + v_1 x^{-1} + \cdots + v_n x^{-n} &= 1 \qquad (v_j \in \mathfrak{m}) \tag{2} \label{eq:5.20-2}
\end{align}
in which we may assume that the degrees $m, n$ are as small as possible. Suppose that $m \geq n$, and multiply \eqref{eq:5.20-2} through by $x^n$:
\begin{equation}\label{eq:5.20-3}
v_0 x^n + v_1 x^{n-1} + \cdots + v_n = x^n. \tag{3}
\end{equation}
Since $v_0 \in \mathfrak{m}$, it follows from \eqref{lem:5.19} that $1 - v_0$ is a unit in $B$, and \eqref{eq:5.20-3} may therefore be written in the form
\[
x^n = w_1 x^{n-1} + \cdots + w_n \qquad (w_j \in \mathfrak{m}).
\]
Hence we can replace $x^m$ in \eqref{eq:5.20-1} by $w_1 x^{m-1} + \cdots + w_n x^{m-n}$, and this contradicts the minimality of the exponent $m$.
\end{proof}

\begin{theorem}\label{thm:5.21}\index{valuation ring!existence}
Let $(B, g)$ be a maximal element of $\Sigma$. Then $B$ is a valuation ring of the field $K$.
\end{theorem}

\begin{proof}
We have to show that if $x \neq 0$ is an element of $K$, then either $x \in B$ or $x^{-1} \in B$. By \eqref{lem:5.20} we may as well assume that $\mathfrak{m}[x]$ is not the unit ideal of the ring $B' = B[x]$. Then $\mathfrak{m}[x]$ is contained in a maximal ideal $\mathfrak{m}'$ of $B'$, and we have $\mathfrak{m}' \cap B = \mathfrak{m}$ (because $\mathfrak{m}' \cap B$ is a proper ideal of $B$ and contains $\mathfrak{m}$). Hence the embedding of $B$ in $B'$ induces an embedding of the field $k = B/\mathfrak{m}$ in the field $k' = B'/\mathfrak{m}'$; also $k' = k[\bar{x}]$ where $\bar{x}$ is the image of $x$ in $k'$, hence $\bar{x}$ is algebraic over $k$, and therefore $k'$ is a finite algebraic extension of $k$.

Now the homomorphism $g$ induces an embedding $\bar{g}$ of $k$ into $\Omega$, since by \eqref{lem:5.19}, $\mathfrak{m}$ is the kernel of $g$. Since $\Omega$ is algebraically closed, $\bar{g}$ can be extended to an embedding $\bar{g}'$ of $k'$ into $\Omega$. Composing $\bar{g}'$ with the natural homomorphism $B' \to k'$, we have, say, $g' \colon B' \to \Omega$ which extends $g$. Since the pair $(B, g)$ is maximal, it follows that $B' = B$ and therefore $x \in B$.
\end{proof}

\begin{corollary}\label{cor:5.22}\index{integral closure!as intersection of valuation rings}
Let $A$ be a subring of a field $K$. Then the integral closure $\overline{A}$ of $A$ in $K$ is the intersection of all the valuation rings of $K$ which contain $A$.
\end{corollary}

\begin{proof}
Let $B$ be a valuation ring of $K$ such that $A \subseteq B$. Since $B$ is integrally closed, by \eqref{prop:5.18}(iii), it follows that $\overline{A} \subseteq B$.

Conversely, let $x \notin \overline{A}$. Then $x$ is not in the ring $A' = A[x^{-1}]$. Hence $x^{-1}$ is a non-unit in $A'$ and is therefore contained in a maximal ideal $\mathfrak{m}'$ of $A'$. Let $\Omega$ be an algebraic closure of the field $k' = A'/\mathfrak{m}'$. Then the restriction to $A$ of the natural homomorphism $A' \to k'$ defines a homomorphism of $A$ into $\Omega$. By \eqref{thm:5.21} this can be extended to some valuation ring $B \supseteq A$. Since $x^{-1}$ maps to zero, it follows that $x \notin B$.
\end{proof}

\begin{proposition}\label{prop:5.23}
Let $A \subseteq B$ be integral domains, $B$ finitely generated over $A$. Let $v$ be a non-zero element of $B$. Then there exists $u \neq 0$ in $A$ with the following property: any homomorphism $f$ of $A$ into an algebraically closed field $\Omega$ such that $f(u) \neq 0$ can be extended to a homomorphism $g$ of $B$ into $\Omega$ such that $g(v) \neq 0$.
\end{proposition}

\begin{proof}
By induction on the number of generators of $B$ over $A$ we reduce immediately to the case where $B$ is generated over $A$ by a single element $x$.

i) Suppose $x$ is transcendental over $A$, i.e., that no non-zero polynomial with coefficients in $A$ has $x$ as a root. Let $v = a_0 x^n + a_1 x^{n-1} + \cdots + a_n$, and take $u = a_0$. Then if $f \colon A \to \Omega$ is such that $f(u) \neq 0$, there exists $\xi \in \Omega$ such that $f(a_0) \xi^n + f(a_1) \xi^{n-1} + \cdots + f(a_n) \neq 0$, because $\Omega$ is infinite. Define $g \colon B \to \Omega$ extending $f$ by putting $g(x) = \xi$. Then $g(v) \neq 0$, as required.

ii) Now suppose $x$ is algebraic over $A$ (i.e.~over the field of fractions of $A$). Then so is $v^{-1}$, because $v$ is a polynomial in $x$. Hence we have equations of the form
\begin{align}
a_0 x^m + a_1 x^{m-1} + \cdots + a_m &= 0 \qquad (a_i \in A) \label{eq:5.23-1}\tag{1} \\
a'_0 v^{-n} + a'_1 v^{1-n} + \cdots + a'_n &= 0 \qquad (a'_i \in A). \label{eq:5.23-2}\tag{2}
\end{align}
Let $u = a_0 a'_0$, and let $f \colon A \to \Omega$ be such that $f(u) \neq 0$. Then $f$ can be extended, first to a homomorphism $h \colon A[u^{-1}] \to \Omega$ (with $h(u^{-1}) = f(u)^{-1}$), and then by \eqref{thm:5.21} to a homomorphism $h \colon C \to \Omega$, where $C$ is a valuation ring containing $A[u^{-1}]$. From \eqref{eq:5.23-1}, $x$ is integral over $A[u^{-1}]$, hence by \eqref{cor:5.22}, $x \in C$, so that $C$ contains $B$, and in particular $v \in C$. On the other hand, from \eqref{eq:5.23-2}, $v^{-1}$ is integral over $A[u^{-1}]$, and therefore by \eqref{cor:5.22} again is in $C$. Therefore $v$ is a unit in $C$, and hence $h(v) \neq 0$. Now take $g$ to be the restriction of $h$ to $B$.
\end{proof}

\begin{corollary}\label{cor:5.24}\index{Nullstellensatz!weak form}
Let $k$ be a field and $B$ a finitely generated $k$-algebra. If $B$ is a field then it is a finite algebraic extension of $k$.
\end{corollary}

\begin{proof}
Take $A = k$, $v = 1$ and $\Omega =$ algebraic closure of $k$.
\end{proof}

\eqref{cor:5.24} is one form of Hilbert's Nullstellensatz. For another proof, see \eqref{prop:nullstellensatz-weak}.

\input{chapter05-exercises.tex}
