\chapter{Noetherian Rings}\label{chapter7}

We recall that a ring $A$ is said to be \emph{Noetherian} if it satisfies the following three equivalent conditions:
\begin{enumerate}
    \item Every non-empty set of ideals in $A$ has a maximal element.
    \item Every ascending chain of ideals in $A$ is stationary.
    \item Every ideal in $A$ is finitely generated.
\end{enumerate}
(The equivalence of these conditions was proved in \eqref{prop:chain-equivalent} and \eqref{prop:noetherian-fg}.)

Noetherian rings are by far the most important class of rings in commutative algebra: we have seen some examples already in Chapter \ref{chapter6}. In this chapter we shall first show that Noetherian rings reproduce themselves under various familiar operations---in particular we prove the famous basis theorem of Hilbert. We then proceed to make a number of important deductions from the Noetherian condition, including the existence of primary decompositions.

\begin{proposition}\label{prop:quotient-noetherian}
    If $A$ is Noetherian and $\phi$ is a homomorphism of $A$ onto a ring $B$, then $B$ is Noetherian.
\end{proposition}

\begin{proof}
    This follows from \eqref{prop:quotient-ring}, since $B \cong A/\mathfrak{a}$, where $\mathfrak{a} = \Ker(\phi)$.
\end{proof}

\begin{proposition}\label{prop:finite-module-noetherian}
    Let $A$ be a subring of $B$; suppose that $A$ is Noetherian and that $B$ is finitely generated as an $A$-module. Then $B$ is Noetherian (as a ring).
\end{proposition}

\begin{proof}
    By \eqref{prop:fg-module}, $B$ is Noetherian as an $A$-module, hence also as a $B$-module.
\end{proof}

\begin{example}\label{ex:gaussian-integers}
    $B = \Z[\mathrm{i}]$, the ring of Gaussian integers. By \eqref{prop:finite-module-noetherian}, $B$ is Noetherian. More generally, the ring of integers in any algebraic number field is Noetherian.
\end{example}

\begin{proposition}\label{prop:localization-noetherian}
If $A$ is Noetherian and $S$ is any multiplicatively closed subset of $A$, then $S^{-1}A$ is Noetherian.
\end{proposition}

    \begin{proof}
    By \eqref{prop:extension-ideals}(i) and \eqref{prop:extension-contraction-properties}(iii), the ideals of $S^{-1}A$ are in one-to-one order-preserving correspondence with the contracted ideals of $A$, hence satisfy the maximal condition. (Alternative proof: if $\mathfrak{a}$ is any ideal of $A$, then $\mathfrak{a}$ has a finite set of generators, say $x_1, \ldots, x_n$, and it is clear that $S^{-1}\mathfrak{a}$ is generated by $x_1/1, \ldots, x_n/1$.)
\end{proof}

\begin{corollary}\label{cor:local-ring-noetherian}
    If $A$ is Noetherian and $\mathfrak{p}$ is a prime ideal of $A$, then $A_{\mathfrak{p}}$ is Noetherian. \qed
\end{corollary}

\begin{theorem}[Hilbert's Basis Theorem]\label{thm:hilbert-basis}
    If $A$ is Noetherian, then the polynomial ring $A[x]$ is Noetherian.
\end{theorem}

\begin{proof}
Let $\mathfrak{a}$ be an ideal in $A[x]$. The leading coefficients of the polynomials in $\mathfrak{a}$ form an ideal $I$ in $A$. Since $A$ is Noetherian, $I$ is finitely generated, say by $a_1, \ldots, a_n$. For each $i = 1, \ldots, n$ there is a polynomial $f_i \in A[x]$ of the form $f_i = a_i x^{r_i} + \text{(lower terms)}$. Let $r = \max_{i=1}^n r_i$. The $f_i$ generate an ideal $\mathfrak{a}' \subseteq \mathfrak{a}$ in $A[x]$.

Let $f = ax^m + \text{(lower terms)}$ be any element of $\mathfrak{a}$; we have $a \in I$. If $m \geq r$, write $a = \sum_{i=1}^n u_i a_i$ where $u_i \in A$; then $f - \sum u_i f_i x^{m-r_i}$ is in $\mathfrak{a}$ and has degree $< m$. Proceeding in this way, we can go on subtracting elements of $\mathfrak{a}'$ from $f$ until we get a polynomial $g$, say, of degree $< r$; that is, we have $f = g + h$, where $h \in \mathfrak{a}'$.

Let $M$ be the $A$-module generated by $1, x, \ldots, x^{r-1}$; then what we have proved is that $\mathfrak{a} = (\mathfrak{a} \cap M) + \mathfrak{a}'$. Now $M$ is a finitely generated $A$-module, hence is Noetherian by \eqref{prop:fg-module}, hence $\mathfrak{a} \cap M$ is finitely generated (as an $A$-module) by \eqref{prop:noetherian-fg}. If $g_1, \ldots, g_m$ generate $\mathfrak{a} \cap M$ it is clear that the $f_i$ and the $g_j$ generate $\mathfrak{a}$. Hence $\mathfrak{a}$ is finitely generated and so $A[x]$ is Noetherian.
\end{proof}

\begin{remark}\label{rem:power-series-noetherian}
It is also true that $A$ Noetherian $\implies$ $A[[x]]$ Noetherian ($A[[x]]$ being the ring of formal power series in $x$ with coefficients in $A$). The proof runs almost parallel to that of \eqref{thm:hilbert-basis} except that one starts with the terms of lowest degree in the power series belonging to $\mathfrak{a}$. See also \eqref{cor:10.27}.
\end{remark}

\begin{corollary}\label{cor:multivariate-polynomial-noetherian}
If $A$ is Noetherian so is $A[x_1, \ldots, x_n]$.
\end{corollary}

\begin{proof}
By induction on $n$ from \eqref{thm:hilbert-basis}.
\end{proof}

\begin{corollary}\label{cor:finitely-generated-algebra-noetherian}
Let $B$ be a finitely-generated $A$-algebra. If $A$ is Noetherian, then so is $B$.

In particular, every finitely-generated ring, and every finitely generated algebra over a field, is Noetherian.
\end{corollary}

\begin{proof}
$B$ is a homomorphic image of a polynomial ring $A[x_1, \ldots, x_n]$, which is Noetherian by \eqref{cor:multivariate-polynomial-noetherian}.
\end{proof}

\begin{proposition}\label{prop:artin-tate}
Let $A \subseteq B \subseteq C$ be rings. Suppose that $A$ is Noetherian, that $C$ is finitely generated as an $A$-algebra and that $C$ is either (i) finitely generated as a $B$-module or (ii) integral over $B$. Then $B$ is finitely generated as an $A$-algebra.
\end{proposition}

\begin{proof}
It follows from \eqref{prop:5.1} and \eqref{cor:5.2} that the conditions (i) and (ii) are equivalent in this situation. So we may concentrate on (i).

Let $x_1, \ldots, x_m$ generate $C$ as an $A$-algebra, and let $y_1, \ldots, y_n$ generate $C$ as a $B$-module. Then there exist expressions of the form
\begin{equation}\label{eq:artin-tate-1}
x_i = \sum_j b_{ij} y_j \qquad (b_{ij} \in B), \tag{1}
\end{equation}
\begin{equation}\label{eq:artin-tate-2}
y_i y_j = \sum_k b_{ijk} y_k \qquad (b_{ijk} \in B). \tag{2}
\end{equation}
Let $B_0$ be the algebra generated over $A$ by the $b_{ij}$ and the $b_{ijk}$. Since $A$ is Noetherian, so is $B_0$ by \eqref{cor:finitely-generated-algebra-noetherian}, and $A \subseteq B_0 \subseteq B$.

Any element of $C$ is a polynomial in the $x_i$ with coefficients in $A$. Substituting~\eqref{eq:artin-tate-1} and making repeated use of~\eqref{eq:artin-tate-2} shows that each element of $C$ is a linear combination of the $y_j$ with coefficients in $B_0$, and hence $C$ is finitely generated as a $B_0$-module. Since $B_0$ is Noetherian, and $B$ is a submodule of $C$, it follows (by \eqref{prop:fg-module} and \eqref{prop:noetherian-fg}) that $B$ is finitely generated as a $B_0$-module. Since $B_0$ is finitely generated as an $A$-algebra, it follows that $B$ is finitely-generated as an $A$-algebra.
\end{proof}

\begin{proposition}\label{prop:nullstellensatz-weak}\index{Nullstellensatz!weak form}
Let $k$ be a field, $E$ a finitely generated $k$-algebra. If $E$ is a field then it is a finite algebraic extension of $k$.
\end{proposition}

\begin{proof}
Let $E = k[x_1, \ldots, x_n]$. If $E$ is not algebraic over $k$ then we can renumber the $x_i$ so that $x_1, \ldots, x_r$ are algebraically independent over $k$, where $r \geq 1$, and each of $x_{r+1}, \ldots, x_n$ is algebraic over the field $F = k(x_1, \ldots, x_r)$. Hence $E$ is a finite algebraic extension of $F$ and therefore finitely generated as an $F$-module. Applying \eqref{prop:artin-tate} to $k \subseteq F \subseteq E$, it follows that $F$ is a finitely generated $k$-algebra, say $F = k[y_1, \ldots, y_s]$. Each $y_j$ is of the form $f_j/g_j$, where $f_j$ and $g_j$ are polynomials in $x_1, \ldots, x_r$.

Now there are infinitely many irreducible polynomials in the ring $k[x_1, \ldots, x_r]$ (adapt Euclid's proof of the existence of infinitely many prime numbers). Hence there is an irreducible polynomial $h$ which is prime to each of the $g_j$ (for example, $h = g_1 g_2 \cdots g_s + 1$ would do) and the element $h^{-1}$ of $F$ could not be a polynomial in the $y_j$. This is a contradiction. Hence $E$ is algebraic over $k$, and therefore finite algebraic.
\end{proof}

\begin{corollary}\label{cor:nullstellensatz-corollary}
Let $k$ be a field, $A$ a finitely generated $k$-algebra. Let $\mathfrak{m}$ be a maximal ideal of $A$. Then the field $A/\mathfrak{m}$ is a finite algebraic extension of $k$. In particular, if $k$ is algebraically closed then $A/\mathfrak{m} \cong k$.
\end{corollary}

\begin{proof}
Take $E = A/\mathfrak{m}$ in \eqref{prop:nullstellensatz-weak}.
\end{proof}

\eqref{cor:nullstellensatz-corollary} is the so-called ``weak'' version of Hilbert's \emph{Nullstellensatz} (= theorem of zeros). The proof given here is due to Artin and Tate. For its geometrical meaning, and the ``strong'' form of the theorem, see the Exercises at the end of this chapter.

\section*{Primary Decomposition in Noetherian Rings}
\addcontentsline{toc}{section}{Primary Decomposition in Noetherian Rings}

The next two lemmas show that every ideal $\neq (1)$ in a Noetherian ring has a primary decomposition.

An ideal $\mathfrak{a}$ is said to be \emph{irreducible}\index{irreducible ideal} if
\[
\mathfrak{a} = \mathfrak{b} \cap \mathfrak{c} \implies (\mathfrak{a} = \mathfrak{b} \text{ or } \mathfrak{a} = \mathfrak{c}).
\]

\begin{lemma}\label{lem:finite-intersection-irreducible}
In a Noetherian ring $A$ every ideal is a finite intersection of irreducible ideals.
\end{lemma}

\begin{proof}
Suppose not; then the set of ideals in $A$ for which the lemma is false is not empty, hence has a maximal element $\mathfrak{a}$. Since $\mathfrak{a}$ is reducible, we have $\mathfrak{a} = \mathfrak{b} \cap \mathfrak{c}$ where $\mathfrak{b} \supsetneq \mathfrak{a}$ and $\mathfrak{c} \supsetneq \mathfrak{a}$. Hence each of $\mathfrak{b}, \mathfrak{c}$ is a finite intersection of irreducible ideals and therefore so is $\mathfrak{a}$: contradiction.
\end{proof}

\begin{lemma}\label{lem:irreducible-primary}
In a Noetherian ring every irreducible ideal is primary.
\end{lemma}

\begin{proof}
By passing to the quotient ring, it is enough to show that if the zero ideal is irreducible then it is primary. Let $xy = 0$ with $y \neq 0$, and consider the chain of ideals $\Ann(x) \subseteq \Ann(x^2) \subseteq \cdots$. By the a.c.c., this chain is stationary, i.e., we have $\Ann(x^n) = \Ann(x^{n+1}) = \cdots$ for some $n$. It follows that $(x^n) \cap (y) = 0$; for if $a \in (y)$ then $ax = 0$, and if $a \in (x^n)$ then $a = bx^n$, hence $bx^{n+1} = 0$, hence $b \in \Ann(x^{n+1}) = \Ann(x^n)$, hence $bx^n = 0$; that is, $a = 0$. Since $(0)$ is irreducible and $(y) \neq 0$ we must therefore have $x^n = 0$, and this shows that $(0)$ is primary.
\end{proof}

From these two lemmas we have at once

\begin{theorem}\label{thm:lasker-noether}
In a Noetherian ring $A$ every ideal has a primary decomposition. \qed
\end{theorem}

Hence all the results of Chapter \ref{chapter4} apply to Noetherian rings.

\begin{proposition}\label{prop:radical-power-contained}
In a Noetherian ring $A$, every ideal $\mathfrak{a}$ contains a power of its radical.
\end{proposition}

\begin{proof}
Let $x_1, \ldots, x_k$ generate $r(\mathfrak{a})$: say $x_i^{n_i} \in \mathfrak{a}$ ($1 \leq i \leq k$). Let $m = \sum_{i=1}^k (n_i - 1) + 1$. Then $r(\mathfrak{a})^m$ is generated by the products $x_1^{r_1} \cdots x_k^{r_k}$ with $\sum r_i = m$; from the definition of $m$ we must have $r_i \geq n_i$ for at least one index $i$, hence each such monomial lies in $\mathfrak{a}$, and therefore $r(\mathfrak{a})^m \subseteq \mathfrak{a}$.
\end{proof}

\begin{corollary}\label{cor:nilradical-nilpotent}
In a Noetherian ring the nilradical is nilpotent.
\end{corollary}

\begin{proof}
Take $\mathfrak{a} = (0)$ in \eqref{prop:radical-power-contained}.
\end{proof}

\begin{corollary}\label{cor:m-primary-equivalent}
Let $A$ be a Noetherian ring, $\mathfrak{m}$ a maximal ideal of $A$, $\mathfrak{q}$ any ideal of $A$. Then the following are equivalent:
\begin{enumerate}[i)]
    \item $\mathfrak{q}$ is $\mathfrak{m}$-primary;
    \item $r(\mathfrak{q}) = \mathfrak{m}$;
    \item $\mathfrak{m}^n \subseteq \mathfrak{q} \subseteq \mathfrak{m}$ for some $n > 0$.
\end{enumerate}
\end{corollary}

\begin{proof}
i) $\implies$ ii) is clear; ii) $\implies$ i) from \eqref{prop:radical-maximal}; ii) $\implies$ iii) from \eqref{prop:radical-power-contained}; iii) $\implies$ ii) by taking radicals: $\mathfrak{m} = r(\mathfrak{m}^n) \subseteq r(\mathfrak{q}) \subseteq r(\mathfrak{m}) = \mathfrak{m}$.
\end{proof}

\begin{proposition}\label{prop:associated-primes-annihilators}
Let $\mathfrak{a} \neq (1)$ be an ideal in a Noetherian ring. Then the prime ideals which belong to $\mathfrak{a}$ are precisely the prime ideals which occur in the set of ideals $(\mathfrak{a}:x)$ ($x \in A$).
\end{proposition}

\begin{proof}
By passing to $A/\mathfrak{a}$ we may assume that $\mathfrak{a} = 0$. Let $\bigcap_{i=1}^n \mathfrak{q}_i = 0$ be a minimal primary decomposition of the zero ideal, and let $\mathfrak{p}_i$ be the radical of $\mathfrak{q}_i$.

Let $\mathfrak{a}_i = \bigcap_{j \neq i} \mathfrak{q}_j \neq 0$. Then from the proof of \eqref{thm:first-uniqueness} we have $r(\Ann(x)) = \mathfrak{p}_i$ for any $x \neq 0$ in $\mathfrak{a}_i$, so that $\Ann(x) \subseteq \mathfrak{p}_i$.

Since $\mathfrak{q}_i$ is $\mathfrak{p}_i$-primary, by \eqref{prop:radical-power-contained} there exists an integer $m$ such that $\mathfrak{p}_i^m \subseteq \mathfrak{q}_i$, and therefore $\mathfrak{a}_i \mathfrak{p}_i^m \subseteq \mathfrak{a}_i \cap \mathfrak{p}_i^m \subseteq \mathfrak{a}_i \cap \mathfrak{q}_i = 0$. Let $m \geq 1$ be the smallest integer such that $\mathfrak{a}_i \mathfrak{p}_i^m = 0$, and let $x$ be a non-zero element in $\mathfrak{a}_i \mathfrak{p}_i^{m-1}$. Then $\mathfrak{p}_i x = 0$, therefore for such an $x$ we have $\Ann(x) \supseteq \mathfrak{p}_i$ and hence $\Ann(x) = \mathfrak{p}_i$.

Conversely, if $\Ann(x)$ is a prime ideal $\mathfrak{p}$, then $r(\Ann(x)) = \mathfrak{p}$ and so by \eqref{thm:first-uniqueness}, $\mathfrak{p}$ is a prime ideal belonging to $0$.
\end{proof}

\input{chapter07-exercises.tex}
