\chapter{Primary Decomposition}\label{chapter4}

The decomposition of an ideal into primary ideals is a traditional pillar of ideal theory. It provides the algebraic foundation for decomposing an algebraic variety into its irreducible components---although it is only fair to point out that the algebraic picture is more complicated than naive geometry would suggest. From another point of view primary decomposition provides a generalization of the factorization of an integer as a product of prime-powers. In the modern treatment, with its emphasis on localization, primary decomposition is no longer such a central tool in the theory. It is still, however, of interest in itself and in this chapter we establish the classical uniqueness theorems.

The prototypes of commutative rings are $\Z$ and the ring of polynomials $k[x_1, \ldots, x_n]$ where $k$ is a field; both these are unique factorization domains. This is not true of arbitrary commutative rings, even if they are integral domains (the classical example is the ring $\Z[\sqrt{-5}]$, in which the element $6$ has two essentially distinct factorizations, $2 \cdot 3$ and $(1 + \sqrt{-5})(1 - \sqrt{-5})$). However, there is a generalized form of ``unique factorization'' of ideals (not of elements) in a wide class of rings (the Noetherian rings).

A prime ideal in a ring $A$ is in some sense a generalization of a prime number. The corresponding generalization of a power of a prime number is a primary ideal. An ideal $\mathfrak{q}$ in a ring $A$ is primary if $\mathfrak{q} \neq A$ and if
\[
    xy \in \mathfrak{q} \implies \text{either } x \in \mathfrak{q} \text{ or } y^n \in \mathfrak{q} \text{ for some } n > 0.
\]
In other words,
\[
    \mathfrak{q} \text{ is primary} \iff A/\mathfrak{q} \neq 0 \text{ and every zero-divisor in } A/\mathfrak{q} \text{ is nilpotent.}
\]

Clearly every prime ideal is primary. Also the contraction of a primary ideal is primary, for if $f \colon A \to B$ and if $\mathfrak{q}$ is a primary ideal in $B$, then $A/\mathfrak{q}^c$ is isomorphic to a subring of $B/\mathfrak{q}$.

\begin{proposition}\label{prop:radical-primary}
Let $\mathfrak{q}$ be a primary ideal in a ring $A$. Then $r(\mathfrak{q})$ is the smallest prime ideal containing $\mathfrak{q}$.
\end{proposition}

\begin{proof}
    By \eqref{prop:nilradical-intersection} it is enough to show that $\mathfrak{p} = r(\mathfrak{q})$ is prime. Let $xy \in r(\mathfrak{q})$, then $(xy)^m \in \mathfrak{q}$ for some $m > 0$, and therefore either $x^m \in \mathfrak{q}$ or $y^{mn} \in \mathfrak{q}$ for some $n > 0$; i.e., either $x \in r(\mathfrak{q})$ or $y \in r(\mathfrak{q})$.
\end{proof}

If $\mathfrak{p} = r(\mathfrak{q})$, then $\mathfrak{q}$ is said to be \emph{$\mathfrak{p}$-primary}\index{p-primary ideal@$\mathfrak{p}$-primary ideal}.

\begin{examples}
    \begin{enumerate}[(1)]
        \item The primary ideals in $\Z$ are $(0)$ and $(p^n)$, where $p$ is prime. For these are the only ideals in $\Z$ with prime radical, and it is immediately checked that they are primary.
        
        \item Let $A = k[x, y]$, $\mathfrak{q} = (x, y^2)$. Then $A/\mathfrak{q} \cong k[y]/(y^2)$, in which the zero-divisors are all the multiples of $y$, hence are nilpotent. Hence $\mathfrak{q}$ is primary, and its radical $\mathfrak{p}$ is $(x, y)$. We have $\mathfrak{p}^2 \subset \mathfrak{q} \subset \mathfrak{p}$ (strict inclusions), so that a primary ideal is not necessarily a prime-power.
        
        \item Conversely, a prime power $\mathfrak{p}^n$ is not necessarily primary, although its radical is the prime ideal $\mathfrak{p}$. For example, let $A = k[x, y, z]/(xy - z^2)$ and let $\bar{x}$, $\bar{y}$, $\bar{z}$ denote the images of $x$, $y$, $z$ respectively in $A$. Then $\mathfrak{p} = (\bar{x}, \bar{z})$ is prime (since $A/\mathfrak{p} \cong k[y]$, an integral domain); we have $\bar{x}\bar{y} = \bar{z}^2 \in \mathfrak{p}^2$ but $\bar{x} \notin \mathfrak{p}^2$ and $\bar{y} \notin r(\mathfrak{p}^2) = \mathfrak{p}$; hence $\mathfrak{p}^2$ is not primary.
    \end{enumerate}
\end{examples}

However, there is the following result:

\begin{proposition}\label{prop:radical-maximal}
    If $r(\mathfrak{a})$ is maximal, then $\mathfrak{a}$ is primary. In particular, the powers of a maximal ideal $\mathfrak{m}$ are $\mathfrak{m}$-primary.
\end{proposition}

\begin{proof}
    Let $r(\mathfrak{a}) = \mathfrak{m}$. The image of $\mathfrak{m}$ in $A/\mathfrak{a}$ is the nilradical of $A/\mathfrak{a}$, hence $A/\mathfrak{a}$ has only one prime ideal, by \eqref{prop:nilradical-intersection}. Hence every element of $A/\mathfrak{a}$ is either a unit or nilpotent, and so every zero-divisor in $A/\mathfrak{a}$ is nilpotent.
\end{proof}

We are going to study presentations of an ideal as an intersection of primary ideals. First, a couple of lemmas:

\begin{lemma}\label{lem:intersection-primary}
    If $\mathfrak{q}_i$ ($1 \leq i \leq n$) are $\mathfrak{p}$-primary, then $\mathfrak{q} = \bigcap_{i=1}^n \mathfrak{q}_i$ is $\mathfrak{p}$-primary.
\end{lemma}

\begin{proof}
    $r(\mathfrak{q}) = r(\bigcap_{i=1}^n \mathfrak{q}_i) = \bigcap r(\mathfrak{q}_i) = \mathfrak{p}$. Let $xy \in \mathfrak{q}$, $y \notin \mathfrak{q}$. Then for some $i$ we have $xy \in \mathfrak{q}_i$ and $y \notin \mathfrak{q}_i$, hence $x \in \mathfrak{p}$, since $\mathfrak{q}_i$ is primary.
\end{proof}

\begin{lemma}\label{lem:colon-primary}\index{colon ideal}
Let $\mathfrak{q}$ be a $\mathfrak{p}$-primary ideal, $x$ an element of $A$. Then
\begin{enumerate}[i)]
    \item if $x \in \mathfrak{q}$ then $(\mathfrak{q} : x) = (1)$;
    \item if $x \notin \mathfrak{q}$ then $(\mathfrak{q} : x)$ is $\mathfrak{p}$-primary, and therefore $r(\mathfrak{q} : x) = \mathfrak{p}$;
    \item if $x \notin \mathfrak{p}$ then $(\mathfrak{q} : x) = \mathfrak{q}$.
\end{enumerate}
\end{lemma}

\begin{proof}
(i) and (iii) follow immediately from the definitions.

(ii): if $y \in (\mathfrak{q} : x)$ then $xy \in \mathfrak{q}$, hence (as $x \notin \mathfrak{q}$) we have $y \in \mathfrak{p}$. Hence $\mathfrak{q} \subseteq (\mathfrak{q} : x) \subseteq \mathfrak{p}$; taking radicals, we get $r(\mathfrak{q} : x) = \mathfrak{p}$. Let $yz \in (\mathfrak{q} : x)$ with $y \notin \mathfrak{p}$; then $xyz \in \mathfrak{q}$, hence $xz \in \mathfrak{q}$, hence $z \in (\mathfrak{q} : x)$.
\end{proof}

A \emph{primary decomposition}\index{primary decomposition} of an ideal $\mathfrak{a}$ in $A$ is an expression of $\mathfrak{a}$ as a finite intersection of primary ideals, say
\begin{equation}\label{eq:primary-decomposition}
    \mathfrak{a} = \bigcap_{i=1}^n \mathfrak{q}_i. \tag{1}
\end{equation}
(In general such a primary decomposition need not exist; in this chapter we shall restrict our attention to ideals which have a primary decomposition.) If moreover (i) the $r(\mathfrak{q}_i)$ are all distinct, and (ii) we have $\mathfrak{q}_i \not\supseteq \bigcap_{j \neq i} \mathfrak{q}_j$ ($1 \leq i \leq n$) the primary decomposition~\eqref{eq:primary-decomposition} is said to be \emph{minimal} (or \emph{irredundant}, or \emph{reduced}, or \emph{normal}, \ldots). By \eqref{lem:intersection-primary} we can achieve (i) and then we can omit any superfluous terms to achieve (ii); thus any primary decomposition can be reduced to a minimal one. We shall say that $\mathfrak{a}$ is \emph{decomposable}\index{decomposable ideal} if it has a primary decomposition.

\begin{theorem}[1st Uniqueness Theorem]\label{thm:first-uniqueness}\index{First Uniqueness Theorem}\index{associated prime ideals}
    Let $\mathfrak{a}$ be a decomposable ideal and let $\mathfrak{a} = \bigcap_{i=1}^n \mathfrak{q}_i$ be a minimal primary decomposition of $\mathfrak{a}$. Let $\mathfrak{p}_i = r(\mathfrak{q}_i)$ $(1 \leq i \leq n)$. Then the $\mathfrak{p}_i$ are precisely the prime ideals which occur in the set of ideals $r(\mathfrak{a} : x)$ $(x \in A)$, and hence are independent of the particular decomposition of $\mathfrak{a}$.
\end{theorem}

\begin{proof}
    For any $x \in A$ we have $(\mathfrak{a} : x) = \left(\bigcap \mathfrak{q}_i : x\right) = \bigcap (\mathfrak{q}_i : x)$, hence $r(\mathfrak{a} : x) = \bigcap_{i=1}^n r(\mathfrak{q}_i : x) = \bigcap_{x \notin \mathfrak{q}_i} \mathfrak{p}_i$ by \eqref{lem:colon-primary}. Suppose $r(\mathfrak{a} : x)$ is prime; then by \eqref{pro:prime avoidance} we have $r(\mathfrak{a} : x) = \mathfrak{p}_j$ for some $j$. Hence every prime ideal of the form $r(\mathfrak{a} : x)$ is one of the $\mathfrak{p}_i$. Conversely, for each $i$ there exists $x_i \notin \mathfrak{q}_i$, $x_i \in \bigcap_{j \neq i} \mathfrak{q}_j$, since the decomposition is minimal; and we have $r(\mathfrak{a} : x_i) = \mathfrak{p}_i$.
\end{proof}
\begin{remarks}\label{rem:first-uniqueness}
    \begin{enumerate}[1)]
        \item The above proof, coupled with the last part of \eqref{lem:colon-primary}, shows that for each $i$ there exists $x_i$ in $A$ such that $(\mathfrak{a} : x_i)$ is $\mathfrak{p}_i$-primary.
        \item Considering $A/\mathfrak{a}$ as an $A$-module, \eqref{thm:first-uniqueness} is equivalent to saying that the $\mathfrak{p}_i$ are precisely the prime ideals which occur as radicals of annihilators of elements of $A/\mathfrak{a}$.
    \end{enumerate}
\end{remarks}

\begin{example}\label{ex:embedded-primes}
    Let $\mathfrak{a} = (x^2, xy)$ in $A = k[x, y]$. Then $\mathfrak{a} = \mathfrak{p}_1 \cap \mathfrak{p}_2^2$ where $\mathfrak{p}_1 = (x)$, $\mathfrak{p}_2 = (x, y)$. The ideal $\mathfrak{p}_2^2$ is primary by \eqref{prop:radical-maximal}. So the prime ideals are $\mathfrak{p}_1$, $\mathfrak{p}_2$. In this example $\mathfrak{p}_1 \subset \mathfrak{p}_2$; we have $r(\mathfrak{a}) = \mathfrak{p}_1 \cap \mathfrak{p}_2 = \mathfrak{p}_1$, but $\mathfrak{a}$ is not a primary ideal.
\end{example}

The prime ideals $\mathfrak{p}_i$ in Theorem~\ref{thm:first-uniqueness} are said to \emph{belong} to $\mathfrak{a}$, or to be \emph{associated} with $\mathfrak{a}$. The ideal $\mathfrak{a}$ is primary if and only if it has only one associated prime ideal. The minimal elements of the set $\{\mathfrak{p}_1, \ldots, \mathfrak{p}_n\}$ are called the \emph{minimal} or \emph{isolated}\index{isolated prime ideal} prime ideals belonging to $\mathfrak{a}$. The others are called \emph{embedded}\index{embedded prime ideal} prime ideals. In the example above, $\mathfrak{p}_2 = (x, y)$ is embedded.

\begin{proposition}\label{prop:minimal-primes}
    Let $\mathfrak{a}$ be a decomposable ideal. Then any prime ideal $\mathfrak{p} \supseteq \mathfrak{a}$ contains a minimal prime ideal belonging to $\mathfrak{a}$, and thus the minimal prime ideals of $\mathfrak{a}$ are precisely the minimal elements in the set of all prime ideals containing $\mathfrak{a}$.
\end{proposition}

\begin{proof}
    If $\mathfrak{p} \supseteq \mathfrak{a} = \bigcap_{i=1}^n \mathfrak{q}_i$, then $\mathfrak{p} = r(\mathfrak{p}) \supseteq \bigcap r(\mathfrak{q}_i) = \bigcap \mathfrak{p}_i$. Hence by \eqref{pro:prime avoidance} we have $\mathfrak{p} \supseteq \mathfrak{p}_i$ for some $i$; hence $\mathfrak{p}$ contains a minimal prime ideal of $\mathfrak{a}$.
\end{proof}

\begin{remarks}
    \begin{enumerate}[1)]
        \item The names \emph{isolated} and \emph{embedded} come from geometry. Thus if $A = k[x_1, \ldots, x_n]$ where $k$ is a field, the ideal $\mathfrak{a}$ gives rise to a variety $X \subseteq k^n$ (see Chapter \ref{chapter1}, Exercise \ref{exer25-chapter1}). The minimal primes $\mathfrak{p}_i$ correspond to the irreducible components of $X$, and the embedded primes correspond to subvarieties of these, i.e., varieties \emph{embedded} in the irreducible components. Thus in the example before \eqref{prop:minimal-primes} the variety defined by $\mathfrak{a}$ is the line $x=0$, and the embedded ideal $\mathfrak{p}_2=(x,y)$ corresponds to the origin $(0,0)$.
        \item It is \emph{not} true that all the primary components are independent of the decomposition. For example $(x^2,xy)=(x)\cap (x,y)^2=(x)\cap (x^2,y)$ are two distinct primary decompositions. However, there are some uniqueness properties: see \eqref{thm:second-uniqueness}.
    \end{enumerate}
\end{remarks}

\begin{proposition}\label{pro:zero-divisors-union-primes}
    Let $\mathfrak{a}$ be a decomposable ideal, let $\mathfrak{a} = \bigcap_{i=1}^n \mathfrak{q}_i$ be a minimal primary decomposition, and let $r(\mathfrak{q}_i) = \mathfrak{p}_i$. Then
    \[
    \bigcup_{i=1}^n \mathfrak{p}_i = \{ x \in A : (\mathfrak{a} : x) \neq \mathfrak{a} \}.
    \]
    In particular, if the zero ideal is decomposable, the set $D$ of zero-divisors of $A$ is the union of the prime ideals belonging to $0$.
\end{proposition}

\begin{proof}
    If $\mathfrak{a}$ is decomposable, then $0$ is decomposable in $A/\mathfrak{a}$: namely $0 = \bigcap \overline{\mathfrak{q}}_i$ where $\overline{\mathfrak{q}}_i$ is the image of $\mathfrak{q}_i$ in $A/\mathfrak{a}$, and is primary. Hence it is enough to prove the last statement of \eqref{pro:zero-divisors-union-primes}. By \eqref{prop:zerodivisors-union} we have $D = \bigcup_{x \neq 0} r(0:x)$; from the proof of \eqref{thm:first-uniqueness}, we have $r(0:x) = \bigcap_{x \notin \mathfrak{q}_j} \mathfrak{p}_j \subseteq \mathfrak{p}_j$ for some $j$, hence $D \subseteq \bigcup_{i=1}^n \mathfrak{p}_i$. But also from \eqref{thm:first-uniqueness} each $\mathfrak{p}_i$ is of the form $r(0:x)$ for some $x \in A$, hence $\bigcup \mathfrak{p}_i \subseteq D$.
\end{proof}

Thus (the zero ideal being decomposable)
\[
\begin{aligned}
D &= \text{set of zero-divisors} \\
&= \bigcup \text{ of all prime ideals belonging to } 0; \\
\mathfrak{N} &= \text{set of nilpotent elements} \\
&= \bigcap \text{ of all minimal primes belonging to } 0.
\end{aligned}
\]

Next we investigate the behavior of primary ideals under localization.

\begin{proposition}\label{prop:localization-primary}\index{localization!of primary ideal}
    Let $S$ be a multiplicatively closed subset of $A$ and $\mathfrak{q}$ a $\mathfrak{p}$-primary ideal.
    \begin{enumerate}[i)]
        \item If $S \cap \mathfrak{p} \neq \varnothing$, then $S^{-1}\mathfrak{q} = S^{-1}A$.
        \item If $S \cap \mathfrak{p} = \varnothing$, then $S^{-1}\mathfrak{q}$ is $S^{-1}\mathfrak{p}$-primary in $S^{-1}A$, and its contraction to $A$ is $\mathfrak{q}$.
    \end{enumerate}

    Hence primary ideals correspond to primary ideals in the correspondence \eqref{prop:extension-ideals} between ideals in $S^{-1}A$ and contracted ideals in $A$.
\end{proposition}
\begin{proof}
    \begin{enumerate}[i)]
        \item If $s \in S \cap \mathfrak{p}$, then $s^n \in \mathfrak{q}$ for some $n$, hence $s^n/1 \in S^{-1}\mathfrak{q}$. Since $s/1$ is a unit in $S^{-1}A$, it follows that $S^{-1}\mathfrak{q} = S^{-1}A$.
        \item If $S \cap \mathfrak{p} = \varnothing$, then $s \in S$ and $as \in \mathfrak{q}$ imply $a \in \mathfrak{q}$, hence $\mathfrak{q}^{ec} = \mathfrak{q}$ by \eqref{prop:extension-ideals}.
        Also from \eqref{prop:extension-ideals} we have $r(\mathfrak{q}^e) = r(S^{-1}\mathfrak{q}) = S^{-1}r(\mathfrak{q}) = S^{-1}\mathfrak{p}$. The verification that $S^{-1}\mathfrak{q}$ is primary is straightforward. Finally, the contraction of a primary ideal is primary. 
    \end{enumerate}
\end{proof}

For any ideal $\mathfrak{a}$ and any multiplicatively closed subset $S$ in $A$, the contraction in $A$ of the ideal $S^{-1}\mathfrak{a}$ is denoted by $S(\mathfrak{a})$.

\begin{proposition}\label{prop:localization-primary-decomposition}
    Let $S$ be a multiplicatively closed subset of $A$ and let $\mathfrak{a}$ be a decomposable ideal. Let $\mathfrak{a} = \bigcap_{i=1}^n \mathfrak{q}_i$ be a minimal primary decomposition of $\mathfrak{a}$. Let $\mathfrak{p}_i = r(\mathfrak{q}_i)$ and suppose the $\mathfrak{q}_i$ numbered so that $S$ meets $\mathfrak{p}_{m+1}, \dots, \mathfrak{p}_n$ but not $\mathfrak{p}_1, \dots, \mathfrak{p}_m$. Then
    \[
    S^{-1}\mathfrak{a} = \bigcap_{i=1}^m S^{-1}\mathfrak{q}_i, \quad S(\mathfrak{a}) = \bigcap_{i=1}^m \mathfrak{q}_i,
    \]
    and these are minimal primary decompositions.
\end{proposition}

\begin{proof}
    $S^{-1}\mathfrak{a} = \bigcap_{i=1}^n S^{-1}\mathfrak{q}_i$ by \eqref{prop:extension-ideals} $= \bigcap_{i=1}^m S^{-1}\mathfrak{q}_i$ by \eqref{prop:localization-primary}, and $S^{-1}\mathfrak{q}_i$ is $S^{-1}\mathfrak{p}_i$-primary for $i = 1, \dots, m$. Since the $\mathfrak{p}_i$ are distinct, so are the $S^{-1}\mathfrak{p}_i$ ($1 \le i \le m$), hence we have a minimal primary decomposition. Contracting both sides, we get
    \[
    S(\mathfrak{a}) = (S^{-1}\mathfrak{a})^c = \bigcap_{i=1}^m (S^{-1}\mathfrak{q}_i)^c = \bigcap_{i=1}^m \mathfrak{q}_i
    \]
    by \eqref{prop:localization-primary} again. 
\end{proof}

A set $\Sigma$ of prime ideals belonging to $\mathfrak{a}$ is said to be \emph{isolated}\index{isolated prime ideal} if it satisfies the following condition: if $\mathfrak{p}'$ is a prime ideal belonging to $\mathfrak{a}$ and $\mathfrak{p}' \subseteq \mathfrak{p}$ for some $\mathfrak{p} \in \Sigma$, then $\mathfrak{p}' \in \Sigma$.

Let $\Sigma$ be an isolated set of prime ideals belonging to $\mathfrak{a}$, and let $S = A - \bigcup_{\mathfrak{p} \in \Sigma} \mathfrak{p}$. Then $S$ is multiplicatively closed and, for any prime ideal $\mathfrak{p}'$ belonging to $\mathfrak{a}$, we have
\begin{align*}
\mathfrak{p}' \in \Sigma &\implies \mathfrak{p}' \cap S = \varnothing; \\
\mathfrak{p}' \notin \Sigma &\implies \mathfrak{p}' \not\subseteq \bigcup_{\mathfrak{p} \in \Sigma} \mathfrak{p} \ (\text{by \eqref{pro:prime avoidance}}) \implies \mathfrak{p}' \cap S \neq \varnothing.
\end{align*}
Hence, from \eqref{prop:localization-primary-decomposition}, we deduce

\begin{theorem}[2nd uniqueness theorem]\label{thm:second-uniqueness}
    Let $\mathfrak{a}$ be a decomposable ideal, let $\mathfrak{a} = \bigcap_{i=1}^n \mathfrak{q}_i$ be a minimal primary decomposition of $\mathfrak{a}$, and let $\{\mathfrak{p}_{i_1}, \dots, \mathfrak{p}_{i_m}\}$ be an isolated set of prime ideals of $\mathfrak{a}$. Then $\mathfrak{q}_{i_1} \cap \cdots \cap \mathfrak{q}_{i_m}$ is independent of the decomposition.
\end{theorem}

In particular:

\begin{corollary}\label{cor:isolated-primary-components-unique}
    The isolated primary components (i.e., the primary components $\mathfrak{q}_i$ corresponding to minimal prime ideals $\mathfrak{p}_i$) are uniquely determined by $\mathfrak{a}$.
\end{corollary}

\begin{proof}[Proof of \eqref{thm:second-uniqueness}]
    We have $\mathfrak{q}_{i_1} \cap \cdots \cap \mathfrak{q}_{i_m} = S(\mathfrak{a})$ where $S = A - \mathfrak{p}_{i_1} \cup \cdots \cup \mathfrak{p}_{i_m}$, hence depends only on $\mathfrak{a}$ (since the $\mathfrak{p}_i$ depend only on $\mathfrak{a}$). 
\end{proof}

\begin{remark}
On the other hand, the embedded primary components are in general not uniquely determined by $\mathfrak{a}$. If $A$ is a Noetherian ring, there are in fact infinitely many choices for each embedded component (see Chapter \ref{chapter8}, Exercise \ref{exer1-chapter8}).
\end{remark}

\input{chapter04-exercises.tex}
